---
title: "Lab 7 - Multiple linear regression"
author: "Grace Bianchi"
date: "11/8/2021"
output: html_document
---

```{r setup, include = TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```

## intro to ggpairs

Use GGally::ggpairs() function tocreate a pairs plot
```{r}
ggpairs(penguins)
```

Create subset
```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g)  %>% # select range using :
  ggpairs(aes(color= species))

ggplot(data = penguins, aes(x = bill_depth_mm, y = body_mass_g, group = species)) +
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```

## Multiple linear regression - penguins 

Use multiple linear regression to try to understand the relationship between multiple predictor variables and a single continuous outcome variable (body mass)

```{r}
# two predictor variables
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins) 

# return just the coefficients
penguin_lm
```

On average, we expect a 51.54 g increase in penguin body mass for each 1 mm increase in flipper length, if everything else is constant.

Use summary() function to get more information:
```{r}
summary(penguin_lm)
```
Bill depth does not have a significant difference from 0.
Adjusted R-squared: 76% of variance in penguin body mass is explained by this model

### Use broom functions tidy and glance

Use broom::tidy to get coefficient summary in a data frame
Use broom::glance to get the model summary in a data frame

```{r}
penguin_lm_tidy <-tidy(penguin_lm)
penguin_lm_tidy
```
In-line code to refer to bill depth coefficient
`r penguin_lm_tidy$estimate[3]`

```{r}
penguin_lm_glance <- glance(penguin_lm)
penguin_lm_glance
```

## Try another model
We have thought really hard, done a literature review, consulted with experts, deeply explored our data, and decided that the 3 most critical variables to include in this model are:

- flipper length
- species
- sex

```{r}
penguins_lm2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)
penguins_lm2
```
Species reference value is Adelie, and the sex reference value is female
mass(g) =  - 365.82 + 20.02(flipper_mm) - 87.63(Chinstrap) + 836.26(Gentoo) + 530.38(male)

If everything else is constant, on average, we expect a Gentoo penguin will be 836.26 g less than chinstrap. 

If everything else is constant, we expect a male penguin, on average, to weigh 530.38 g more than a female.

### Use broom:augment() to see predicted values 

For existing data, predict what the body mass would be given a flipper length
```{r}
augment(penguins_lm2)
```
## Use plot() to look at model diagnostics

```{r}
plot(penguins_lm2)
```
Scale-location - vertical spread across entire length of predicted values
Residuals vs leverage - points outside cook's distance should be investigated,
may be an outlier pulling more than its weight

- Conceptual understanding and expertise allows me to responsibly determine that penguin species, sex, and flipper length are responsable predictor variables ( make sure to think about variables and different variable combinations)
- Diagnostic plots all check out for normality of residuals, homoscedasticity, and no worrisome outliers (<< last one is not an assumption)

## Make output tables

Using modelsummary:
```{r}
modelsummary(penguins_lm2)
```

Using stargazer:
```{r, results = "asis"}
stargazer(penguins_lm2, type = "html")
```

